---
title: "Predicting stopping distance for cars"
subtitle: "1920 Cars dataset from R documentation"
author: "Carlos Calderon"
date: "December 17, 2016"
output: 
  ioslides_presentation: 
    fig_height: 4
    fig_width: 7
    highlight: kate
    transition: faster
widescreen: true
autosize: true
font: 'helvetica'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

This is the final project of developing data products by Coursera. 

The objective of my shiny app is to predict the stopping distance in feet of a 1920 car by using the speed in mph as input from the user (YOU). 

The following slides will explain the HOW of my shiny app "CarDataset Prediction". 

Source:
Cars dataset from orginal R documentation.

## Data Processing
We can see that the data is a simple data frame with two variables, speed [mph] and distance [feet].
```{r,comment ="", warning=FALSE, message=FALSE}
# Load data set
head(cars)

```

## Plot the data
Based on the scatterplot of the data, a linear fit is a reasonable place to start to obtain a prediction.

```{r,comment="", warning=FALSE, message=FALSE}
plot (cars)
```

## Fit a linear model
We observe an okay fit of our model to the data.
```{r,comment="",warning=FALSE, message=FALSE}
model<-lm(dist ~ speed, data = cars)
par(mfrow = c(2,2))
plot(model)
```

## Give it a try!

Here is the URL to my shiny app, enjoy!

http://cacalderon.shinyapps.io/CarDatasetPrediction

If the link does not work for you, try to copy and paste in your web browser. 

```{r,comment="",warning=FALSE, message=FALSE}
# http://cacalderon.shinyapps.io/CarDatasetPrediction
```

The UI.R and Server.R files for the shiny app can be found in GitHub

https://github.com/cacalderon/Data-Products-Final-Project

If the link does not work for you, try to copy and paste in your web browser. 

```{r,comment="",warning=FALSE, message=FALSE}
# https://github.com/cacalderon/Data-Products-Final-Project
```


